Document Classification

### 2018-11-02 DATA607/Project_4.Rmd
Additional work on Project 4

get_message <- function(full_path){
  message <- ''
  header_finished <- FALSE
  # Open the file
  con <- file(full_path, blocking = FALSE)
  # Go line by line
  for(line in readLines(con)){
    # Order matters.  I don't want to lead with the blank line between the header
    if(header_finished){
      message <- paste(message, line)
    }
    # Look for the end of the header
    if(line == ""){
      header_finished <- TRUE
    }
  }
  # Close the connection to the file
  close(con)

  # Change text to lower case 
  message <- tolower(message)
  # Remove all punctuation
  message <- gsub("[[:punct:][:blank:]]+", " ", message)
  # Tokenize message
  words <- scan_tokenizer(message)
  # Remove stop words
  stop_words <- tm::stopwords()
  words <- words[!words %in% stop_words]
  # Stem words using hunspell
  words <- unlist(lapply(words, stem_hunspell))

  return(words)
}

@@

bag_of_words <- get_message(full_path)
df <- data.frame(word = bag_of_words, count = c(1)) %>%
  group_by(word) %>%
  summarise(count = sum(count)) %>%
  ungroup() %>%
  mutate(file = example_file, type = "spam")
```

>>>>

process_message <- function(full_path){
  message <- ''
  n_lines <- 0
  header_finished <- FALSE
  # Open the file
  con <- file(full_path, blocking = FALSE)
  # Go line by line
  for(line in readLines(con)){
    # Order matters.  I don't want to lead with the blank line between the header
    if(header_finished){
      n_lines <- n_lines + 1
      message <- paste(message, line)
    }
    # Look for the end of the header
    if(line == ""){
      header_finished <- TRUE
    }
  }
  # Close the connection to the file
  close(con)

  # Change text to lower case 
  n_characters <- nchar(message)
  lower_message <- tolower(message)
  n_capital_letters <- adist(message, lower_message)[[1]]
  # Remove all punctuation
  clean_message <- gsub("[[:punct:][:blank:]]+", " ", lower_message)
  n_punctuation_marks <- adist(lower_message, clean_message)[[1]]
  # Tokenize message
  words <- tm::scan_tokenizer(clean_message)
  # Remove stop words
  #stop_words <- tm::stopwords()
  #words <- words[!words %in% stop_words]
  # Stem words using hunspell
  #words <- unlist(lapply(words, stem_hunspell))

  return(list(words = words, characters = n_characters, capital_letters = n_capital_letters, punctuation_marks = n_punctuation_marks, lines = n_lines))
}

@@

results <- process_message(full_path)
#df <- data.frame(word = bag_of_words, count = c(1)) %>%
#  group_by(word) %>%
#  summarise(count = sum(count)) %>%
#  ungroup() %>%
#  mutate(file = example_file, type = "spam")
```
